A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-19 manuscript.Rmd
open port internally only #41

The second option is to start the container in the background and to interact with the container via the web browser and the RStudio server instance running in it. In order to do so, you need to supply a password to log into the RStudio server (`-e PASSWORD=<YOUR_PASS>`) and open a network service on a specified port (`-p 8787:8787`).

```{bash, eval=FALSE}
docker run -e PASSWORD=<YOUR_PASS> -p 8787:8787 image-name
```

>>>>

The second option is to start the container in the background and to interact with the container via the web browser and the RStudio server instance running in it. In order to do so, you need to supply a password to log into the RStudio server (`-e PASSWORD=<YOUR_PASS>`) and open a network service on a specified port (`-p 127.0.0.1:8787:8787`).

```{bash, eval=FALSE}
docker run -e PASSWORD=<YOUR_PASS> -p 127.0.0.1:787:8787 image-name
```
